Summer 2025 ToDo

### 2025-06-12 Relations/Paper/Summer_2025_TODO.tex
Update with email todos

\section*{Week starting 2nd June}
\begin{todolist}
  \item Should we add quantification to each definition(I think quantification for $a$ is already implied)? E.g.\\
  \item [\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.\\
   Transforms to
  \item[\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$ for all $b, c, d \in A$.
  \item For showing inc -> RP we're currently just saying "This is immediate". Is this sufficient? We did have a proof previously but I think we removed it for space reasons.
  \item Remove "desired implications" and similar organizational issues in the code (general review)
  \item Consider defining FB in terms of existing list library; especially in the rebooted repo,
  we shouldn't use manual List type just for this.
  \item Move all definitions and properties from Section 2.3 to Seq.agda, except Inc.
  \item Revise section 3.1
\end{todolist}
\end{document}

>>>>

\section*{Week starting 2nd June}
\begin{todolist}
  \item Should we add quantification to each definition(I think quantification for $a$ is already implied)? E.g.\\
  \item [\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.\\
   Transforms to
  \item[\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$ for all $b, c, d \in A$.
  \item For showing inc -> RP we're currently just saying "This is immediate". Is this sufficient? We did have a proof previously but I think we removed it for space reasons.
  \item Remove "desired implications" and similar organizational issues in the code (general review)
  \item Consider defining FB in terms of existing list library; especially in the rebooted repo,
  we shouldn't use manual List type just for this.
  \item Move all definitions and properties from Section 2.3 to Seq.agda, except Inc.
  \item Revise section 3.1
\end{todolist}
\section*{Week starting 9th June (some of these items taken from Dr. Polonsky's email sent June 6th)}
\begin{todolist}
  \item [\done] Thm. 19(iv), i don't like that the parens are italicized.  maybe it would be okay if instead of CR => CP we just write "the forward implication"
  \item [\done] Proof of (iii), line 296: do we really need () around SN?
  \item Page 9, second half (the hierarchy): we should add a proof that $\MF \cap \SN \iff \NF$, say this in the text, and note that this does NOT hold for $\SM$ and $\WN$.  Hence, the tables include a separate column for their combination.
  \item  In the par before 4.1 counterexamples, add that in the global table, the counterexample 3 satisfies the hypotheses globally.
(I actually wonder whether we need example 9 at all, if we have a counterexample to the global one.  Am I missing something?). \sacomment{I don't think we need to expand that CE:3 satisfies the global hypotheses. I'm hoping that we've done enough to show to the reader how to read the table at this point. If you disagree I'm happy to add it in though. As to why have local and global counterexamples, good point. Unless either of us can think of a reason we'll remove in the next meeting.}
    \item [\done] the * and dagger in the table should be explained in the caption, or in the text.
    \sacomment{I prefer to have this as a footnote. I have put it as a caption for now but I would revert it to what we had before.  }
\end{todolist}
\end{document}
